### 2023-02-06 definitions.tex
up

Since $t$-liveness is undecidable for reset Petri-Nets that are WSTS with strong monotony, from Proposition \ref{reductions}, and since Reset Petri Net $t$-liveness is undecidable,  we deduce that resilience is undecidable for WSTS with strong monotony.

>>>>

Since $t$-liveness is undecidable for reset Petri-Nets that are WSTS with strong monotony, from Proposition \ref{reductions},  we deduce that resilience is undecidable for WSTS with strong monotony.
